Objective-first optimization for nanophotonics

### 2011-07-29 presentations/group-pres_2011-08-04.tex
Edited field constraint section. Changed pictures to jpeg format.

\BIT \itemsep -1pt
\item adjoint method
\item objective-first approach
\item field constraints: boundary-value problem
\item structure constraints: level-set formulation
\item example
\item ongoing and future work
\EIT

@@

\BIT
\item this problem is still non-convex, use linear approximation 
\begin{align}
r(x_0+dx,p_0+dp) & \approx r(x_0,p_0) + \pf{r}{x} dx + \pf{r}{p} dp \\
f(x_0+dx) & \approx f(x_0) + \pf{f}{x} dx 
\end{align}
\item decrease $r$ by choosing $dp \propto -\pf{r}{p}$
\item decrease $r$ by choosing 
    $dx \propto - (I - P_{f_x}) \pf{r}{x}$
\item $P_{f_x}$ is the projector onto the vector space defined by $\pf{f}{x}$, this satisfies the equality constraint
\item computing $P_{f_x}$ requires solving for $\left(\pf{f}{x}^T \pf{f}{x}\right)^{-1}$, but this is often \emph{trivial}
\EIT
\newpage

@@

\oursection{Field constraints: boundary-value problem}
\BIT
\item formulation of the constraint is the key issue
\item a sufficient constraint for most devices is to match field values along the border
\BEQ f(x) = \| x^\text{border} - x^\text{border}_0 \|^2 = 0 \EEQ
\item physics residual is the error in Maxwell's sourceless, time-harmonic equations
\BEQ \|g(x,p)\|^2 = \|A(p)x\|^2 = 
    \left\| \left[ 
    \begin{array}{cc}
        \nabla\times & i\mu\omega \\
        -ip\omega & \nabla\times
    \end{array}
    \right] 
    \left[ \begin{array}{c} x_E \\ x_H \end{array} \right] 
    \right\|^2
\EEQ
\item here $p$ determines the values of $\epsilon$
\EIT
\newpage

\BIT
\item to experiment, we fix $p = p_0$, which convexifies the ob-1 formulation
\begin{align}
\mbox{minimize} & \quad \|A(p_0)x\|^2 \\
\subjectto & \quad x^\text{border} = x^\text{border}_0
\end{align}
\begin{center}
\includegraphics[width=0.8\textwidth]{../figures/waveguide.png}
\end{center}
\item here, $p_0$ is a waveguide structure, and the design objective is a perfect waveguide mode at input and output
\EIT
\newpage

\BIT
\item for general structures and design objectives, this results in a ``soft physics'' field solve
\begin{center}
\includegraphics[width=0.8\textwidth]{../figures/crossbar.png}
\end{center}
\item matlab files available at \url{https://github.com/JesseLu/wave-tools}, look for \texttt{em\_bval\_2dte/demo.m}
\EIT
\newpage

\BIT
\item
\EIT

>>>>

\BIT \itemsep -1pt
\item adjoint method
\item objective-first approach
\item field constraint: boundary-value problem
\item structure constraint: level-set formulation
\item example
\item ongoing and future work
\EIT

@@

\BIT
\item this problem is still non-convex, use linear approximation 
\begin{align}
r(x_0+dx,p_0+dp) & \approx r(x_0,p_0) + \pf{r}{x} dx + \pf{r}{p} dp \\
f(x_0+dx) & \approx f(x_0) + \pf{f}{x} dx 
\end{align}
\item decrease $r$ by choosing $dp \propto -\pf{r}{p}$
\item decrease $r$ by choosing 
    $dx \propto - (I - P_{f_x}) \pf{r}{x}$
\item $P_{f_x}$ is the projector onto the vector space defined by $\pf{f}{x}$, used to satisfy equality constraint
\item computing $P_{f_x}$ requires solving for $\left(\pf{f}{x}^T \pf{f}{x}\right)^{-1}$, but this is often \emph{trivial}
\EIT
\newpage

@@

\oursection{Field constraint: boundary-value problem}
\BIT
\item our problem is
\begin{align}
\mbox{decrease} & \quad \|g(x,p)\|^2 \\
\subjectto & \quad f(x) = 0
\end{align}
\item physics residual is the error in Maxwell's sourceless, time-harmonic equations
\BEQ \|g(x,p)\|^2 = \|A(p)x\|^2 = 
    \left\| \left[ 
    \begin{array}{cc}
        \nabla\times & i\mu\omega \\
        -ip\omega & \nabla\times
    \end{array}
    \right] 
    \left[ \begin{array}{c} x_E \\ x_H \end{array} \right] 
    \right\|^2
\EEQ
\item here $p$ determines the values of $\epsilon$
\EIT
\newpage

\BIT
\item key issue: formulation of the constraint
\item a sufficient constraint for most devices is to match field values along the border
\BEQ f(x) = \| x^\text{border} - x^\text{border}_0 \|^2 = 0 \EEQ
\begin{center}
\includegraphics[width=0.8\textwidth]{../figures/waveguide.jpg}
\end{center}
\item here, $p$ is a waveguide structure, and the design objective is a perfect waveguide mode at input and output
\EIT
\newpage

\BIT
\item to experiment, we fix $p = p_0$, which convexifies the ob-1 formulation
\begin{align}
\mbox{minimize} & \quad \|A(p_0)x\|^2 \\
\subjectto & \quad x^\text{border} = x^\text{border}_0
\end{align}
\item for general structures and design objectives, this results in a ``soft physics'' field solve
\begin{center}
\includegraphics[width=0.8\textwidth]{../figures/crossbar.jpg}
\end{center}
\EIT
\newpage

\BIT
\item prioritizing the design objective means we allow physics to be ``bent''
\item here, reflected waves from the junction magically disappear as they approach the border
\begin{center}
\includegraphics[width=0.8\textwidth]{../figures/mode_converter.jpg}
\end{center}
\item matlab files available at \url{https://github.com/JesseLu/wave-tools}, look for \texttt{em\_bval\_2dte/demo.m}
\EIT

\oursection{Structure constraint: level-set method}
\BIT
\item a more detailed statement of our problem is
\begin{align}
\mbox{decrease} & \quad \|g(x,p)\|^2 \\
\subjectto & \quad f(x) = 0 \\
        & \quad p \in \{p_\text{can be made}\}
\end{align}
\item need to constrain possible $p$ to what can be fabricated
\item for nanophotonics this means two distinct materials only
\item using $p \in \{\epsilon_1, \epsilon_2\}$ defeats the purpose of using linear approximations
\item need to \emph{incrementally} update the topology of the structure
\EIT
